### 2021-05-09 papers/SYRCoSE/overview.tex
overview.tex: article

To facilitate computable semantics, we define a subclass of
finitely supported event structures as a finite sequence of events
combined with finitely supported function which enhances events with 
additional information, such as their labels, causality predecessors, \etc 
Encoding finitely supported functions is not a trivial endeavor in
a proof assistant and for this task we use the \finmap~%
\footnote{\url{https://github.com/math-comp/finmap}}
library which is an extension of \mathcomp providing finite sets and
finite maps on types with a choice operator (rather than on finite types).

>>>>

To facilitate computable semantics, we define a subclass of
finitely supported event structures as a finite sequence of events
combined with a finitely supported function which enhances events with 
additional information, such as their labels, causality predecessors, \etc 
Encoding finitely supported functions is not a trivial endeavor in
a proof assistant and for this task we use the \finmap~%
\footnote{\url{https://github.com/math-comp/finmap}}
library which is an extension of \mathcomp providing finite sets and
finite maps on types with a choice operator (rather than on finite types).
